---
title: "Notes on weighted density map development"
output: html_document
author: "CSev"  
date: "`r format(Sys.Date())`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This R Markdown document is meant to show my progess and development of maps that show weighted density in the United States. It is as much an exercise for me to learn a different set of development tools than I have traditionally used. My experience is with Matlab and Stata, and I would like to develop similar proficiency in R. Further, I implement a workflow that includes use of [GitHub](http://www.github.com).

Because some difficulties I've previously experience with spatial data in R, I will try to use the [sf](https://cran.r-project.org/web/packages/sf/vignettes/sf1.html) (simple features) package for all this work.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
